---
title: "Assignment 4 DATA 712"
author: "Michael Manigault"
date: "2/24/2021"
output: html_document
---

```{r}
rm(list=ls())
gc()
directory <-"C:/Users/Mike Jr/Downloads/"
setwd(directory)
```



```{r}
GSSExtract <- read.csv("C:/Users/Mike Jr/Downloads/GSSExtract.txt")
GSSExtract
```
```{r}
library(tidyr)
data.tidy <- gather(GSSExtract, AGE, SEX, MARITAL)
data.tidy
```



```{r}
summary(GSSExtract)
```

```{r}
prop.table(table(GSSExtract$SEX))
```

```{r}
prop.table(table(GSSExtract$MARITAL))
```

```{r}
prop.table(table(GSSExtract$DEGREE))
```
```{r}
prop.table(table(GSSExtract$CONFINAN))
```
```{r}
prop.table(table(GSSExtract$CONBUS))
```

## Question A
The median age of the respondent is 50 years old.

##Question B
Approximately 55% of the sample is female.

##Question C
The proportion of high school dropouts is greater than the proportion of graduate school graduates.

##Question D
Approximately 17% of the respondents are divorced.

##Question E
CONFINAN has the highest proportion of people who have a "great deal" of faith in that institution. 


